THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-11 DishReflectometry/Paper1_v1.tex
Added feed figure.

\begin{figure*}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure*}

@@

The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%%%%%%%%%%%%%%%
\section{Measurements}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $4.5m$
($\sim{14.76}$ft).

@@

where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$. $I_{meas}$ is the auto correlated power obtained from a single HERA element. Upon our assumption that two adjacent antenna elements have identical electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence. The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed. Therefore, in this case, $\Gamma_{d} < 1$. For a given baseline $\vec b$, taking the ratio of the measured power and the incident power,

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
   \label{eq8}
\end{eqnarray}

@@

%%%%%%%%%%%%%%%%%
\subsection{Method}
The instrument response kernel is measured by measuring the return loss of the antenna element at the output port of the feed using a vector network analyser. The vector network analyser transmits a broadband noise of known amplitude and phase via a $75ft$ cable up to the feed. While a part of this signal  is returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space. However, the reflected signal from the dish vertex returns to
the feed. This incident signal is now
reflected back and forth in between the feed and the dish much like the sky
signal reflection discussed previously.

If $I_{tr}$ is the signal transmitted by the VNA , $\Gamma_{f}$ is the feed reflection coefficient, $I_{r}$
is the power incident back on the feed after reflection from the dish then the reflected power, $I_{refl}$,
back into the VNA would be:
\begin{equation}\label{eqn:series2}
I_{refl} =  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

@@

\begin{equation}
I_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}
\end{equation}

@@

\begin{eqnarray}
I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
 & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}

>>>>

\begin{figure*}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure*}

@@

The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%%%%%%%%%%%%%%%
\section{Measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}

We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $4.5m$
($\sim{14.76}$ft).

@@

%where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$.

$I_{meas}$ is the auto correlated power obtained from a single HERA element. Upon our assumption that two adjacent antenna elements have identical electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence. The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed. Therefore, in this case, $\Gamma_{d} < 1$. For a given baseline $\vec b$, taking the ratio of the measured power and the incident power,

\begin{eqnarray}\label{eqn:ratio1}
{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\fngexp]^{n}
   \nonumber\\
   \label{eq8}
\end{eqnarray}

@@

%%%%%%%%%%%%%%%%%
\subsection{Method}
The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser. The vector network analyser transmits a broadband noise of known amplitude and phase via a $50ft$ cable up to the feed. While a part of this signal  is returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space. However, the reflected signal from the dish vertex returns to
the feed. This incident signal is now
reflected back and forth in between the feed and the dish much like the sky
signal reflection discussed previously.

If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $\(1-\Gamma_{f})$ fraction would be radiated. This radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection. If  $I_{r}$ is the
is the total reflected power incident back on the feed after n reflection from the dish then the total reflected power, $I_{refl}$,
back into the VNA would be:
\begin{eqnarray}\label{eqn:series2}
I_{refl} & = &  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} \fngexp + (\Gamma_{f}\Gamma_{d})^2 (\fngexp)^{2}\nonumber\\
&&+ ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{2}]
\end{eqnarray}

@@

\begin{equation}
I_{r}= \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}
\end{equation}

@@

\begin{eqnarray}
I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
 &&  + \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d}\fngexp \nonumber\\
&& +  ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{n}]\nonumber\\
 \end{eqnarray}
